Experiment 4 of 4

### 2018-08-11 experiments/E_exp_3/writeup/E_exp_3.Rmd
D_exp_3
Only added an Rproj and a jpg and html

<figure>
<img src="./flow-of-experiment4.pdf" alt="Mountain View" style="width:480px;height:300px;">
<figcaption>Flow of experiment 4.</figcaption>
</figure>

>>>>

<figure>
<img src="./E_exp_3-flow.jpg" alt="flow-of-D_exp_3" style="width:480px;height:300px;">
<figcaption>Flow of experiment E_exp_3.</figcaption>
</figure>
